Correlation between different emission channels from an atom inside a leaky driven cavity\\ \thanks{corresponding author e-mail: guillermopreisser@hotmail.com}

### 2019-11-14 paper1.2.1.tex
Muchos cambios de Pablo al texto. Falta conclusiones

\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cacity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, .
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

We now summarize te quantum trajectory formalism \cite{bla} that we
use to solve the system. We start with a state which represents a
ground state of the atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
Using a non-hermitian Hamiltonian will have as a consequence that the
probability won't be conserved \cite{Sakurai:1167961}. The evolution
of the state through the schrödinger equation will be interrupted by a
quantum jump – an abrupt change on our state in which a photoemission
has ocurred. The probability for such quantum jump to happen will be
given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{eqnarray} \label{relprob}
\delta p_1 &=& \gamma \bra{\phi (t)} \sigma_+
               \sigma_-\ket{\psi (t)}\delta t \\
  \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi (t)}\delta t 
\end{eqnarray}
We use these collapse probabilities to simulate the quantum
trajectories, where we compare the collapse probability of eq.
\eqref{probcol} with a random number $\epsilon$, uniformly distributed
between zero and one. In the case the condition $\delta p > \epsilon$
is fulfilled we simulate that a quantum jump has happened, by acting
with one of the collapse operators. The operator with which we'll act
on the state will be given according to the relative probabilities of
eq. \eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
Using equation \eqref{probcol} one can easily identify the
corresponding collapse probabilities of the system. Having identified
the collapse operators and the collapse probability, we simulate
quantum trajectories, in which we keep count of the number of quantum
jumps for each collapse operator, relating the number of quantum jumps
associated to spontaneous emissions for each number of quantum jumps
associated to cavity emissions until we reach a maximum number of
cavity emissions, which we establish. The procedure of register of
emissions is summarized in algorithm \ref{alg1}.

Realizing a large number of these trajectories, storing the registers
in a matrix, where we keep track of the number of times that there
were certain number of spontaneous emissions for each different number
of cavity emission, enable us to obtain probability distributions that
relate these two quantities.

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we use the quantum trajectory formalism to calculate
the distribution probability of the number of spontaneous emissions by
the atom conditioned to the number of photons that leaked the cavity
from its mirror .
\subsection{Probability distributions of emissions}

In Fig.\ref{probdiss} we see the probability of obtaining different number of spontaneous emissions for different number of cavity emissions. It is clear from the plot that our probability distributions are going to be more spread out as more time (and hence more cavity emissions) pass.

@@

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\subsection{Extracting data from the probability distributions}
Due to the complex dynamic of the driven Jaynes-Cummings system \cite{Carmichael1993Open}, it is important to know the dynamic that the system undergoes at the moment of obtaining the probability distributions, in order to have a better physical understanding of our results. In this case we opt for fixing the number of photons in the cavity.

We do this by solving what is known as the Maxwell-Bloch equations, which give the dynamic of our system for the variables  $\expval{a}, \expval{\sigma_-}$ and $\expval{\sigma_z}$ that correspond to the cavity field, atomic coherence, and atomic inversion respectively \cite{Alsing_1991}. For the case of the driven Jaynes-Cummings system, these equations are given by
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined  $z = e^{i\omega t}\expval{a}$, $v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$. Solving for the case in which our variables are constant we can obtain steady state solutions \cite{gagniuc2017markov}.  From \eqref{bloch1} one can obtain the equation
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} + g\expval{\sigma_-}_{ss}}{\kappa}.
\end{equation}
While from \eqref{bloch2} and \eqref{bloch3} one obtains
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}.
\end{equation}
The requirement that both \eqref{chaf1} and \eqref{chaf2} are valid gives as result
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1 + \frac{2g^2}{\gamma \kappa}\frac{1}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2.
\end{equation}
Considering $\gamma \gg g$, it is possible to clear $|\expval{a}|^2$, which allow us to obtain an expression for the expected value of the number of photons in the cavity
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 = \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}
\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

\section{Correlation between photons emitted in different channels}\label{sc:correlation}
So far we have obtained estimations for the number of spontaneous emission for each measured number of cavity emissions. From our results it is obvious how the number of spontaneous emissions will increase with respect to the number of cavity emissions, given that more time will pass and more emissions will occur. One can also see how increasing the cavity linewidth $\kappa$ and keeping the other parameters constant will translate into a decrease of spontaneous emissions with respect to the number of cavity emissions. However, one question remains: is there a direct correlation between these two quantities? If yes, how this varies with respect to the cavity linewidth. From the beginning one could expect that in the case for a big $\kappa$ there would be no correlation at all, since this situation will be equivalent to the situation where there is no cavity.

In order to have a measure of the correlation of the emissions we introduce the Pearson Correlation Coefficient \cite{benesty2009pearson}
\begin{equation} 
r_{xy} = \frac{\sum\limits_{i=1}^n(x_i - \bar{x})(y_i - \bar{y})}{\sqrt{\sum\limits_{i=1}^n(x_i - \bar{x})^2\sum\limits_{i=1}^n(y_i - \bar{y})^2}}.  \label{correlationc}
\end{equation}
Having an equation that gives us a measure of the correlation, now we want the necessary data in order to obtain information about the correlation between the two types of emissions that we deal with. We can obtain this data by defining a temporal interval from which we make a register of the final number of spontaneous and cavity emissions. Given that what we are doing are essentially stochastic calculations, there will be variations in the final number of emissions for each trajectory. Making a large number of trajectories keeping track of the final number of emissions and pluggin the data in \eqref{correlationc} we are able to calculate the correlation.

@@

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases
From Fig. \ref{corrxy} we see that, as we expected, the correlation goes to zero as we increase the cavity linewidth. Nonetheless, perhaps a more interesting question is: how high can this correlation be? Trying with values for $\kappa/\gamma$ lower than $0.1$, we notice that the correlation's increase stops and a decrease begins. It is possible that this stop in the increase of the correlation is due to the fact that if we keep decreasing the cavity linewidth it will come a point where the number of emissions will decrease considerably, diminishing the correlation. If this is the case we should expect that as we increase the temporal intervals, %the cavity linewidth at which the correlation starts decreasing should be smaller.
we also see an increment of the correlation.

@@

In Fig. \ref{errorzz} we can appreciate that, as we increase the total temporal interval, there is also a slight increase in the correlation. This supports the idea that the time that takes for the system in stablishing the number photons will affect the value for the correlation, for values of $\kappa/\gamma$ lower than $0.1$.

\section{Conclusions}\label{sc:conclusions}
In this work we considered a driven Jaynes-Cummings system. We made a program in which, through the use of quantum trajectory theory, we were able to obtain probability distributions that relate the number of spontaneous emissions given certain number of cavity emissions. Through the probability distributions we obtained estimations for the number of spontaneous emissions by measuring cavity emissions, considering the correspondent error. Finally we study the existing correlation where we saw how this correlation decreases as we increase the cavity linewidth. However, if we try with values for  $\kappa/\gamma < 0.1$, there comes a point where the increase stops and we see a decrease. We believe this is related to the fact that if we use enough small values of $\kappa$ there will come a point where the emission of photons will be too low and this will imply a decrease in the correlation. The results in this work provide a tool that could be useful in the manipulation of single photons product of spontaneous emission, and provide insight into the physical behavior of the driven Jaynes-Cummings model.

>>>>

\section{Driven Jaynes-Cummings model}\label{sc:drivenjc}
We consider a system consisting of a two-level atom, coupled to a mode
of a leaky cavity. The mode is driven by a coherent field resonant
with the atomic transition and the cavity mode.
% In order to account for
% dissipation one may use a non-hermitian Hamiltonian to describe the
% system \cite{bla}. Using this description for the system will turn
% useful at the moment of using quantum trajectory theory. Such
% Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The Hamiltonian of this system, in the rotating wave approximation is
given by
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent
field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where the annihilation operator $a$ of a single photon in the cavity,
and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The
operators $\sigma_-, \sigma_+$ account for the atomic lowering and
raising operators, respectively, and the operator $\sigma_z$ accounts
for the population difference between the atomic levels. These
operators obey
$[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp
2\sigma_\pm$. The strength of the coupling between atom and cavity
field is given by the constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
where $V_Q$ is the mode volume , $d$ is the atomic dipole , and
$\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term
proportional to the coherent field amplitude. Dissipation is
introduced by the following non-hermitian Hamiltonian
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to spontaneous emission of the atom and cavity losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a\, ,
\end{equation}
\end{subequations}
where $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay
rate. The evolution between jumps is given by $H=H_s+H_{nh}$. This
evolution is interrumped by spontaneus emission by the atom or when a
photon leaks the cavity.

We now summarize te quantum trajectory formalism \cite{bla} that we
use to solve the system. Each quantum trajectory is simulated as
folllows. We start with a state which represents a ground state of the
atom with no photons in the cavity,
$\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it
with the Schrödinger equation through some time $\delta t$, using the
non-hermitian Hamiltonian
\begin{equation}
H = H_s +H_{nh}\, .
\end{equation}
The evolution of the state through the schrödinger equation will be
interrupted by a quantum jump – an abrupt change on our state in which
a photoemission has ocurred. The probability for such quantum jump to
happen, during the time step $\delta t$, is given by the collapse
probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where

\begin{subequations}\label{relprob}
  \begin{eqnarray}  \delta p_1 &=& \gamma \bra{\phi
      (t)} \sigma_+
                                                  \sigma_-\ket{\psi (t)}\delta t\, , \\
    \delta p_2 &=& 2\kappa \bra{\phi (t)} a^\dagger a\ket{\psi
                   (t)}\delta t \, .
  \end{eqnarray}
\end{subequations}
We compare the collapse probability of Eq.~\eqref{probcol} with a
random number $\epsilon$, uniformly distributed between zero and one.
In the case the condition $\delta p > \epsilon$ is fulfilled we
simulate that a quantum jump has happened, by acting with one of the
collapse operators $a$ or $\sigma_-$ and renormalizating the obtained
state. The operator that will act on the state will be given according
to the relative probabilities of Eqs.~\eqref{relprob}.
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
If $\delta p > \epsilon$ is not fulfilled we just renormalize the
state, because using a non-hermitian Hamiltonian will have as a
consequence that the probability won't be conserved
\cite{Sakurai:1167961}. For the next step we repeat the procedure
using the resulting state for this step. One quantum trajectory of
total time $t$ is obtained after repeating the previous procedure
$t/\delta t$ steps. For each trajectory we count the number of quantum
jumps, the jumps correponding to operator $a$ reduces the number of
photons inside the cavity and corresponds to a photon that leak the
cavity. The jumps corresponding to operator $\sigma_-$ interrumps its
unitary evolution and send it back to the ground state, it corresponds
to a spontaneous emission. The procedure to register emissions in the
two different channels is summarized in algorithm \ref{alg1}.

We realize a large number of these trajectories and keep track of the
numbers of emission for each channel, with this data we can calculate
probability distributions that relate these two quantities.

\section{Counting photons emitted in different channels}\label{sc:distributions}
In this section we calculate the probability distribution of the
number of spontaneous emissions, $n_s$, under different conditions.
First we calculate the distribution probability of $n_s$ when we know
the number of leaked photons from the cavity, $n_c$; we use
$p(n_s|n_c)$ to denote the distribution. Using this function we can
investigate the correlation between $n_s$ and $n_c$ as a function of
the cavity decay rate. This correlation is a measure of how much
information we can obtain about $n_s$ if we know $n_c$.

The number of total photon emissions depends on how fast the atom is
excited. In order to do a meaningful comparison when we change
$\kappa$, we adjust the cavity drive so the mean number of photons
inside the cavity is the same. If we keep $g$ constant this guarantees
that the rate of atomic excitation is the same for different $\kappa$.

In order to find the value of the cavity drive $\mathcal{E}$ as a
function of the mean value of photons inside the cavity, we solve the
Maxwell-Bloch equations. These equations give the dynamic of our
system for the variables $\expval{a}, \expval{\sigma_-}$ and
$\expval{\sigma_z}$ that correspond to the cavity field, atomic
coherence, and atomic inversion respectively \cite{Alsing_1991}. For
the case of the driven Jaynes-Cummings system, these equations are
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined $z = e^{i\omega t}\expval{a}$,
$v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$.
When the system is stable, we obtain, from
\eqref{maxbloch}, the steady state
solutions \cite{gagniuc2017markov}
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} +
  g\expval{\sigma_-}_{ss}}{\kappa}\, ,
\end{equation}
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\, ,
\end{equation}
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1
+ \frac{2g^2}{\gamma \kappa}\frac{1}{1 +
  \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2\, .
\end{equation}
When $\gamma \gg g$, the expected value of the number of photons in
the cavity is 
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 \approx \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}

\paragraph{The case when the number of photons leaked from the cavity  is known}
\fxnote{No esta claro que hiciste aqui. Segun yo corriste el programa
  distinto tiempo para cada caso}
We calculate the distribution probability of the number of spontaneous
emission conditioned to the number of photons detected leaking the
cavity. We assume that the mean flux of photons in each channel is
known in advance (they can be calculated knowing the cavity drive).
The results are shown in Fig.\ref{probdiss}. As the number of leaked
photons increases, the mean number of spontaneous emissions increases.
This result is expected, because the number of leaked photons is
correlated with the time we are counting spontaneus emission photons
from a driven atom: the larger the number of leaked photons the larger
the time we measure spontaneous emitted photons which implies a larger
mean number of emitted photons. Also, the probability distribution is
wider when the number of leaked photons increases, this implies less
accuracy guessing the number of spontaneus emission as the number of
leaked photons increases. If we know the cavity drive, this results
does not imply that we can learn something extra about the number of
spontaneous emissions knowing the number of photons leaked from the
cavity; it is clear that when we increase the time window where we
count photons, both, the number of leaked photons and the number of
spontaneous emissions, increases.

In section~\ref{sc:correlation} we will show
when there is correlation between emissions in the two channels.

@@

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\paragraph{The case where the time we measure photons is fixed}

We know fix the time we measure photons, which is equivalente to
fixing the mean number of spontaneous emited photons or the mean number
of leaked photons from the cavity.

We focus in the case where we fix the mean number of photons inside
the cavity. This number depends on the cavity drive and the atomic
parameters.

\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

\section{Correlation between photons emitted in different channels}\label{sc:correlation}
In this section we study the correlation between the number of
spontaneus emission from the atom, $n_s$, and the number of photons
that leak the cavity, $n_c$, as a function of the cavity decay rate,
$\kappa$. We expect that when $\kappa\rightarrow\infty$ there would be
no correlation between these two random variables, since this
situation will be equivalent to the situation where there is no
cavity.

In order to have a measure of the correlation between emissions in the
two different channels, we use the Pearson Correlation Coefficient
\cite{benesty2009pearson}
\begin{equation} 
r_{n_s,n_c} = \frac{\sum\limits_{i=1}^n(n_s^{(i)} -
  \bar{n}_s)(n_c^{(i)} - \bar{n}_c)}{\sqrt{\sum\limits_{i=1}^n(n_s^{(i)}
    - \bar{n}_s)^2\sum\limits_{i=1}^n(n_c^{(i)} - \bar{n}_c)^2}}\, ,  \label{correlationc}
\end{equation}
where $n^{(i)}$ is the output $i$ of the random variable $n$.

@@

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.45]{million2.pdf}
\caption{\small{Correlation using different temporal intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}
%kncrease or increases

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

In Fig. \ref{errorzz} it is shown that as we increase the temporal
interval where we count photons, we also see a small increment of the
correlation, due to the fact that more photons leaks the cavity
giving information about the system.
\fxnote{Hay que mejorar las graficas. Las variables tienen que ser
  mayores y las unidades estan mal}

@@

\section{Conclusions}\label{sc:conclusions}
Differently to the case of an atom in free space, we can learn
something about the number of spontaneus emissions done by an atom
into different electromagnetic modes if the atom is inside a leaky
cavity.

In this work we considered a driven Jaynes-Cummings system. We made a
program in which, through the use of quantum trajectory theory, we
were able to obtain probability distributions that relate the number
of spontaneous emissions given certain number of cavity emissions.
Through the probability distributions we obtained estimations for the
number of spontaneous emissions by measuring cavity emissions,
considering the correspondent error. Finally we study the existing
correlation where we saw how this correlation decreases as we increase
the cavity linewidth. However, if we try with values for
$\kappa/\gamma < 0.1$, there comes a point where the increase stops
and we see a decrease. We believe this is related to the fact that if
we use enough small values of $\kappa$ there will come a point where
the emission of photons will be too low and this will imply a decrease
in the correlation. The results in this work provide a tool that could
be useful in the manipulation of single photons product of spontaneous
emission, and provide insight into the physical behavior of the driven
Jaynes-Cummings model.
